%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
	{Business Engineer and IT Consultant} % Job title
	{Freelancer} % Organization
	{Hamburg - Germany} % Location
	{oct. 2016 - now} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Helping SMEs and start-ups to automate their businesses}
			\item {Supporting business development, sales engineering}
			\item {Finding solutions to technical challenges}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
    {Business Analyst and controller} % Job title
    {Videobeat Networks} % Organization
    {Hamburg - Germany} % Location
    {sep. 2015 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Carried the responsibility for one R\&D project and the new ERP integration}
        \item {Developed several P.o.C. for clients}
        \item {Supported the french business dev. team in Paris + follow up}
        \item {Managed the DevOps and added several new tools to the company portfolio}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Intern} % Job title
    {Videobeat Networks} % Organization
    {Hamburg - Germany} % Location
    {Feb 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Master-thesis (ROI Tracking: How to build an uplift model in order to better understand visit attribution from a TV marketing campaign)}
        \item {Debugged python tools and REST APIs developed by the company}
        \item {Supported the french business dev. team based in Hamburg}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Search Engine Marketing Intern} % Job title
    {Ciao, Leguide Group} % Organization
    {Munich - Germany} % Location
    {Sep. 2013 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Launched and optimized german SEM campaigns}
        \item {Monitored results and R.O.I. with Adobe SiteCatalyst and Google Analytics}
        \item {Created VBA tools to improve efficiency and processes}
      \end{cvitems}
    }
%---------------------------------------------------------
	\cventry
	{Business Development Intern} % Job title
	{Selfresto} % Organization
	{Montbéliard - France} % Location
	{Nov. 2012 - Jan 2013} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Launched business development and signed the first deals (partner acquisition)}
			\item {Upgraded the customer acquisition strategy}
		\end{cvitems}
	}
%---------------------------------------------------------
  \cventry
    {Freelance} % Job title
    {Self-employed} % Organization
    {France} % Location
    {2012 - 2014} % Date(s)
    {	
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item{Business development, online marketing and consulting (IT) for Startups and SMEs}
      \end{cvitems}
    }




%---------------------------------------------------------
\end{cventries}
